Benchmarking neuromorphic systems with Nengo

### 2015-09-14 paper/rebuttals.txt

> No

> The introduction gives a clear motivation for the work in the
> article, but it does not state which works have been done previously
> on that topic. For example, there are several articles investigating
> accuracy in neuromorphic hardware for specific benchmark
> problems. As three of the backends are software-based, it would also
> be appropriate here to cite prior work on accuracy/speed in neural
> software simulators.

We have added two paragraphs to the introduction citing prior work
benchmarking SpiNNaker, FACETS, and Brian,
and situating this study in that context in lines 19-35.
They read:

  Prior work benchmarking neural simulators and neuromorphic hardware
  has focused on low-level neural performance.  For example,
  \citet{sharp2013} showed that SpiNNaker can simulate a recurrent
  network of leaky integrate-and-fire neurons with similar firing rate
  and inter-spike intervals as the NEST neural simulator, but around
  six times faster.  \citet{stromatias2013} showed that SpiNNaker's
  power consumption varies between 15 and 37 Watts (0.5--0.8 Watts per
  chip) depending on the number of neurons being simulated.
  \citet{goodman2008brian} showed that Brian simulated a randomly
  connected network of 4000 leaky integrate-and-fire twice as fast as
  an equivalent Matlab implementation, but around three times slower
  than a C implementation. In all of these cases, none of the networks
  elicited activity that could be directly related to experimentally
  recorded data on a behavioral task.

@@

  The box shows the median and interquartile range, while the whiskers
  extend to the farthest data point within 1.5 times the interquartile
  range; outliers are shown above and below the whiskers.

As noted in these captions, we have also now included the outliers.
We were initially concerned that outliers would make the rest of the
boxplot too small relative to the expanded axes caused by outliers.
However, we now feel that including all of the data makes these
boxplots more useful.

> Some of the results in Fig. 7 are puzzling: For BG sequence*, the
> run time for nengo and nengo_ocl is even higher without probes
> (compared to Fig. 6), being well outside the 95% confidence
> intervals. This should be explained.

Reviewer 1 noticed this effect as well.
Our reply was as follows:

### 2015-09-14 paper/paper.tex
Incorporate feedback from Chris

Prior work benchmarking neural simulators
and neuromorphic hardware has focused
on low-level neural performance.
For example, \citet{sharp2013}
showed that SpiNNaker can simulate
a recurrent network of leaky integrate-and-fire neurons
with similar firing rate and inter-spike intervals
as the NEST neural simulator,
but around six times faster.
\citet{stromatias2013} showed that
SpiNNaker's power consumption varies
between 15 and 37 Watts
(0.5--0.8 Watts per chip)
depending on the number of neurons
being simulated.
\citet{goodman2008brian} showed that
Brian simulated a randomly connected
network of 4000 leaky integrate-and-fire
twice as fast as an equivalent Matlab implementation,
but around three times as slow as
a C implementation.
In all of these cases,
none of the networks
elicited activity that could be
directly related to experimentally recorded data
on a behavioral task.

@@

Unlike software backends,
considerable effort is taken
to translate a Nengo model into
something that can run on a SpiNNaker board.
Fortunately, SpiNNaker can be reprogrammed
as it is composed of a large collection
of chips, each with 18 ARM processing cores.
In particular, this allows SpiNNaker
to take advantage of Nengo's
encoding and decoding capabilities,
greatly reducing the amount of RAM needed
\citep{mundy2015}.
The SpiNNaker backends accomplishes this
by using decoded values to determine
changes to the input currents to each neuron,
rather than using purely
spike-based transmission.
However, a previous implementation
of a Nengo SpiNNaker backend
\citep{galluppi2012}
used primarily spike-based communication,
only making an explicit signal-to-spike
encoding at the beginning
of the network and an explicit
spike-to-signal decoding
at the end of a network.
Neuromorphic hardware that
can only communicate through spikes
can be made to interact with Nengo
through explicit encoding and decoding processes
like the one used in \citealp{galluppi2012},
or by using Nengo on the host machine
to explicitly generate spike patterns
that are communicated to the device.
However, these methods may introduce
additional noise in the simulation,
resulting in inaccuracies.

>>>>

Prior work benchmarking neural simulators
and neuromorphic hardware has focused
on low-level neural performance.
For example, \citet{sharp2013}
showed that SpiNNaker can simulate
a recurrent network of leaky integrate-and-fire neurons
with similar firing rate and inter-spike intervals
as the NEST neural simulator,
but around six times faster.
\citet{stromatias2013} showed that
SpiNNaker's power consumption varies
between 15 and 37 Watts
(0.5--0.8 Watts per chip)
depending on the number of neurons
being simulated.
\citet{goodman2008brian} showed that
Brian simulated a randomly connected
network of 4000 leaky integrate-and-fire
twice as fast as an equivalent Matlab implementation,
but around three times slower than
a C implementation.
In all of these cases,
none of the networks
elicited activity that could be
directly related to experimentally recorded data
on a behavioral task.

@@

Unlike software backends,
considerable effort is taken
to translate a Nengo model into
something that can run on a SpiNNaker board.
Fortunately, SpiNNaker can be reprogrammed
as it is composed of a large collection
of chips, each with 18 ARM processing cores.
In particular, this allows SpiNNaker
to take advantage of Nengo's
encoding and decoding capabilities,
greatly reducing the amount of RAM needed
\citep{mundy2015}.
The SpiNNaker backends accomplishes this
by using decoded values to determine
changes to the input currents to each neuron,
rather than using purely
spike-based transmission.
However, neuromorphic hardware that
can only communicate through spikes
can be made to interact with Nengo
through explicit encoding and decoding processes
on the chip, as was done in \citealp{galluppi2012},
or by using Nengo on the host machine
to explicitly generate spike patterns
that are communicated to the device,
as was done in \citealp{choudhary2012}.
However, these methods may introduce
additional noise in the simulation,
resulting in inaccuracies.
